\chosentitle

### 2024-10-08 paper/main.tex
some updates

\documentclass[modern]{aastex631}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{MnSymbol}

@@

\section*{}\noindent\todo{
Known issues to resolve before submission:\\
- Show basis vectors from HARPS instead of APOGEE\\
- Update HARPS fits to use blaze-corrected flux (only AB-type stars use it now)\\
- Update SNR vs precision to show shaded distribution instead of a single percentile\\
- Add citations\\
- Figure 2 doesn't have the telluric model in it, re-fit and make pretty\\
- Update red text.
}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{harps-alfCenA-example.pdf}
    \caption{An example fit to a single \eso/\harps\ spectrum of Alpha Centauri A (black), showing the continuum fits per echelle order (dark blue), the stellar absorption model (blue) and the \todo{telluric transmission model (light blue)}, all fit simultaneously. Near the strong Ca H and K lines (right panels) it is clear that there are \emph{no} `continuum pixels' in those echelle orders, yet the model provides an excellent estimate of the true continuum. \label{fig:alf-cen-A-example}}
\end{figure*}

@@

A separate reason for model-data disagreement comes from our use of the telluric transmission model. The telluric models available to us are of lower spectral resolution ($\mathcal{R} \sim 25{,}000$) than \harps. This is apparent when closely comparing the fitted model with the data (e.g., if one could zoom in finely to Figure~\ref{fig:alf-cen-A-example}), but it is otherwise not obvious. The model telluric transmission predicts features that are clearly broader than the data, but the telluric basis vectors are a sufficiently good description for the data that the telluric absorption does not get captured by the continuum basis vectors and adversely affect the fit.\\

@@

\begin{figure}
    \caption{Distribution (shaded) of rectified flux of $\alpha$-Centauri A as a function of S/N ratio, with every spectrum fit independently. The line represents the 95th percentile, where the scatter in this percentile is 0.46\% for spectra with S/N $>$ 30, and 0.22\% for everything with S/N $>$ 100. \label{fig:alpha-cen-wrt-snr}}
\end{figure}

@@

There are not many literature metrics to choose from when evaluating performance of continuum normalization. We have qualitatively shown the distribution of rectified flux values for $\alpha$-Centauri A, and quantitatively estimated the precision from the scatter in the 95th percentile of rectified flux values. These statistics are computed using all wavelengths, but it is well-known that continuum is easier to model at redder optical wavelengths because there are fewer absorption features. One excellent examination of continuum normalization consistency is that of \citet{RASSINE}, where they report consistent continuum normalization at the level of 2\% based on applications to extremely high quality ($S/N > 1000$) \eso/\harps\ spectra of $\alpha$-Centauri B stacked over consecutive nights, and 0.29\% for a comparably high quality spectrum of the Sun. Their statistic is defined as the 2$\sigma$ of $1-f_i$, where $f_i$ is the $i$th normalized flux value at the anchor point locations used to build the continuum. The anchor points are chosen by the user, which makes for a less direct comparison with our statistic, but for these purposes we will assume that the continuum anchor points are perfectly chosen and truely represent the continuum in the star. Given these assumptions, for comparison purposes we take \texttt{RASSINE} as providing 1\% consistency in continuum estimates for S/N $> 1000$ spectra of $\alpha$-Centauri B, and 0.15\% consitency for comparable Solar spectra. If they restrict their statistic to wavelengths redder than 4500,\AA, their precision for $\alpha$-Centauri B improves to 0.6\%. In comparison, for spectra we use that is 1/10th the S/N ratio, we find our method yields consistent continuum estimates at the level of 0.22\%.\\

>>>>

\documentclass[modern]{aastex631}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{MnSymbol}
\usepackage{rotating}

@@

\section*{}\noindent\todo{
Known issues to resolve before submission:\\
- Show basis vectors from HARPS instead of APOGEE\\
- Update HARPS fits to use blaze-corrected flux (only AB-type stars use it now)\\
- In the "alpha Cen A" sample, sometimes they accidentally observed alpha Cen B and didn't realise! Maybe better to use a different star?\\
- Add citations\\
- Update red text.
}

@@

\begin{sidewaysfigure}
    \includegraphics[width=\textwidth]{example.pdf}
    \caption{An example fit to a single \eso/\harps\ spectrum of HD~222595 (black), showing the continuum fits per echelle order (dotted), the stellar absorption model (red) and the telluric transmission model (blue), all fit simultaneously with a constrained linear absorption model. Near the strong Ca H and K lines it is clear that there are \emph{no} `continuum pixels' in those echelle orders, yet the model provides an excellent estimate of the true continuum. \label{fig:example-echelle}}
\end{sidewaysfigure}

@@

A separate reason for model-data disagreement comes from our use of the telluric transmission model. The telluric models available to us are of lower spectral resolution ($\mathcal{R} \sim 25{,}000$) than \harps. This is apparent when closely comparing the fitted model with the data (e.g., if one could zoom in finely to Figure~\ref{fig:example-echelle}), but it is otherwise not obvious. The model telluric transmission predicts features that are clearly broader than the data, but the telluric basis vectors are a sufficiently good description for the data that the telluric absorption does not get captured by the continuum basis vectors and adversely affect the fit.\\

@@

\begin{figure}
    \includegraphics*[width=\textwidth, height=3in]{alpha-cen-repeat-snr.pdf}
    \caption{Distribution (shaded) of rectified flux of $\alpha$-Centauri A as a function of S/N ratio, with every spectrum fit independently. The line represents the 95th percentile, where the scatter in this percentile is 0.46\% for spectra with S/N $>$ 30, and 0.22\% for everything with S/N $>$ 100. \label{fig:alpha-cen-wrt-snr}}
\end{figure}

@@

There are not many literature metrics to choose from when evaluating performance of continuum normalization. We have qualitatively shown the distribution of rectified flux values for $\alpha$-Centauri A, and quantitatively estimated the precision from the scatter in the 95th percentile of rectified flux values. These statistics are computed using all wavelengths, but it is well-known that continuum is easier to model at redder optical wavelengths because there are fewer absorption features. One excellent examination of continuum normalization consistency is that of \citet{RASSINE}, where they report consistent continuum normalization at the level of 2\% based on applications to extremely high quality ($S/N > 1000$) \eso/\harps\ spectra of $\alpha$-Centauri B stacked over consecutive nights, and 0.29\% for a comparably high quality spectrum of the Sun. Their statistic is defined as the 2$\sigma$ of $1-f_i$, where $f_i$ is the $i$th normalized flux value at the anchor point locations used to build the continuum. The anchor points are chosen by the user, which makes for a less direct comparison with our statistic, but for these purposes we will assume that the continuum anchor points are perfectly chosen and truely represent the continuum in the star. Given these assumptions, for comparison purposes we take \texttt{RASSINE} as providing 1\% consistency in continuum estimates for S/N $> 1000$ spectra of $\alpha$-Centauri B, and 0.15\% consitency for comparable Solar spectra. If they restrict their statistic to wavelengths redder than 4500\,\AA, their precision for $\alpha$-Centauri B improves to 0.6\%. In comparison, for spectra we use that is 1/10th the S/N ratio, we find our method yields consistent continuum estimates at the level of 0.22\%.\\

%\todo{I really don't want to, but should I Fisher information matrix and predict how precisely we could estimate the continuum as a function of S/N for this model? It's linear so it's simple, but it adds necessitates a lot of explanatory text that is not easily digestible by my target audience (spectroscopists).}\\
